ST563 Final Project

### 2021-03-11 ST563-FP.Rmd
finished boosting description

The main benefit of using boosting is to reduce overfitting. It often yields the best results in terms of the ensemble learning methods. 
## Multiple Linear Regression

>>>>

The main benefit of using boosting is to reduce overfitting. It often yields the best results in terms of the ensemble learning methods. Like the random forest model, since boosting is an ensemble learning technique, it will have a lower variance than other methods. Also, there is no need to scale down variables or create any dummy variables for categorical variables. All that said, boosting is not without its shortcomings; it does not do well with high dimensionality, it's not very interpretable (since it is a sort of blackbox algorithm), and it is relatively expensive computationally.

## Multiple Linear Regression
